% !TeX encoding = UTF-8
% !TeX spellcheck = sk_SK
% !TeX root=tukedip.tex
%%
\begin{thebibliography}{19}
\addcontentsline{toc}{section}{\numberline{}Zoznam použitej
literatúry}

\harvarditem{P. Aparicio, and P. Lima.}{1999}{aparicio}
Aparicio. P. and Lima. P. 1999. \emph{Autonomous Distributed Control of a Population of Cooperative Robots}.

% \harvarditem{M. Koes, I. Nourbakhsh, and K. Sycara.}{2005}{koes}
% M. Koes, I. Nourbakhsh, and K. Sycara. 2005. \emph{Heterogeneous Multi-Robot Coordination with Spatial and
% Temporal Constraints}. Proceedings of the Twentieth National Conference on Artificial Intelligence and the
% Seventeenth Innovating Applications of Artificial Intelligence Conference. pp. 1292-1297.

\harvarditem{J. McLurkin.}{1996}{mclurkin}
J. McLurkin. 1996. \emph{Using Cooperative Robots for Explosive Ordance Disposal.}. IEEE Explore [Electronic
Journal]

\harvarditem{Ke Xu}{2010}{kexu}
Ke Xu. 2010. \emph{Integrating Centralized and Decentralized Approaches for Multi-Robot Coordination}

\harvarditem{V. Grassi Junior. et al.}{2006}{grassi}
V. Grassi Junior. et al. 2006. \emph{Hybrid deliberative/reactive architecture for human-robot interaction}. ABCM Symposium Series in Mechatronics 2. pp. 563–570.

\harvarditem{E. Rimon, D. Koditschek}{1992}{rimon}
E. Rimon, D. Koditschek. 1992. \emph{Exact robot navigation using artficial potential flelds}. IEEE Transactions on Robotics and Automation 8. pp. 501–518.

\harvarditem{R. A. Brooks}{1985}{brooks}
R. A. Brooks. 1985. \emph{A robust layered control system for a mobile robot}. IEEE Journal of Robotics and Automation 2. pp. 14–23.

\harvarditem{N. L´echevin, C. Rabbath, P. Sicard}{2006}{lechavin}
N. L´echevin, C. Rabbath, P. Sicard. 2006. \emph{Trajectory tracking of leader-follower formations characterized by constant line-of sight angles}. Automatica 42. pp. 2131–2141.

\harvarditem{T. Gustavi, X. Hu}{2008}{gustavi}
T. Gustavi, X. Hu. 2008. \emph{Observer-based leader-following formation control using onboard sensor information}. IEEE Transactions on Robotics 24. pp. 1457–1462.

\harvarditem{T. Balch, R. Arkin}{1998}{balch}
T. Balch, R. Arkin. 1998. \emph{Behavior-based formation control for multi robot teams}. IEEE Transactions on Robotics and Autmation.

\harvarditem{L. Parker}{1996}{parker}
L. Parker. 1996. \emph{On the design of behavior-based multi-robot teams}. Journal of Advanced Robotics 10. pp. 547–578.

\harvarditem{K. D. Do}{2007}{do}
K. D. Do. 2007. \emph{Formation tracking control of unicycle-type mobile robots}. IEEE International Conference on Robotics and Automation. pp. 527–538.

\harvarditem{X. Li, J. Xiao, Z. Cai}{2005}{li}
X. Li, J. Xiao, Z. Cai. \emph{Backstepping based multiple mobile robots formation control}. IEEE International Conference on Intelligent Robots and Systems. pp. 887 – 892.

\harvarditem{R. C. Arkin.}{1992}{arkin}
R. C. Arkin. 1992. \emph{Cooperation without communication: Multiagent schema-based robot navigation}. Journal of Robotic Systems, pp. 351–364.

\harvarditem{M. Mataric.}{1994}{mataric}
M. Mataric. 1994. \emph{Interaction and Intelligent Behavior}. PhD thesis, MIT, EECS.

\harvarditem{J. Wang.}{1994}{wang}
J. Wang. 1994. \emph{On sign-board based inter-robot communication in distributed robotic systems}. In IEEE ICRA, pp. 1045–1050.

\harvarditem{J. Wang and G. Beni.}{1990}{wbeni}
J. Wang and G. Beni. 1990. \emph{Distributed computing problems in cellular robotic systems}. In IEEE/RSJ IROS, pp. 819–826.

\harvarditem{ A. Matsumoto, H. Asama, Y. Ishida, K. Ozaki, and I. Endo.}{1990}{matsumoto}
A. Matsumoto, H. Asama, Y. Ishida, K. Ozaki, and I. Endo. 1990. \emph{Communication in the autonomous and decentralized robot system: ACTRESS}. In IEEE/RSJ IROS. pp. 835–840.

\harvarditem{K. Jin, P. Liang, and G. Beni.}{1994}{jin}
K. Jin, P. Liang, and G. Beni. 1994. Stability of synchronized distributed control of discrete swarm structures. In IEEE ICRA, pp. 1033–1038.

\harvarditem{P. Caloud, W. Choi, J.-C. Latombe, C. Le Pape, and M. Yin.}{1990}{caloud}
P. Caloud, W. Choi, J.-C. Latombe, C. Le Pape, and M. Yin. 1990. \emph{Indoor automation with many mobile robots}. In IEEE/RSJ IROS. pp. 67–72.

\harvarditem{L. E. Parker.}{1994}{parek}
L. E. Parker. 1994. \emph{ALLIANCE: an architecture for fault tolerant, cooperative control of heterogeneous mobile robots}. In IEEE/RSJ IROS. pp. 776–783.

\harvarditem{S. Garrido-Jurado, R. Munoz-Salinas, F.J. Madrid-Cuevas, M.J. Marin-Jimenez}{2014}{garido}
S. Garrido-Jurado, R. Munoz-Salinas, F.J. Madrid-Cuevas, M.J. Marin-Jimenez. 2014. \emph{Automatic generation and detection of highly reliable 
fiducial markers under occlusion}.

\harvarditem{Webots}{2021}{webots}
Webots. Neuronics IPR. https://cyberbotics.com/doc/guide/introduction-to-webots. [Online; accessed April 21, 2021].

\end{thebibliography}